---
title: "iBreakDown intro"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Read data

```{r}
titanic <- read.table("titanic_bd.csv", sep=",", header = T)
head(titanic)
```

# Train a model

```{r}
library("randomForest")
rf <- randomForest(Survived ~ Pclass + Sex + Age, data = titanic[,c(2:5)])
```

# Create explainer

```{r}
library("DALEX")
library("iBreakDown")

explainer_rf <- explain(rf,
                        data = titanic[,c(3:5)],
                        y = titanic$Survived)
```

# Create instance level explanation

2-years old boy that travels in the second class

```{r}
titanic[274,]
predict(rf, titanic[274,])
```

# Sequential attributions

## Scenario 1

It's a boy so smaller survival.
He traveled in the second class so even lower survival (negative).
But he is very young do odds are higher (positive), **most passangers in the second class are adults**.

```{r}
(exp_1 <- local_attributions(explainer_rf, titanic[274,], order=c(2, 1,3)))
plot(exp_1)
```

## Scenario 2

It's a boy so smaller survival.
He is very young so odds are higher (positive).
And he traveled in the second class so odds are even more higher (positive), **most kids are from the third class**.

```{r}
(exp_2 <- local_attributions(explainer_rf, titanic[274,], order=c(2, 3,1)))
plot(exp_2)
```

# With interactions

Effect of age depends on passanger class. 

```{r}
(exp_3 <- local_interactions(explainer_rf, titanic[274,]))
plot(exp_3)
```

